---
title: "Compare fundamentals"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r, include = FALSE}

library(here)
library(colorSpec)
library(data.table)
library(ggplot2)
library(magrittr)
library(openxlsx)

i_am("R/calculationNeil.Rmd")

source(here("R", "functions.R"))

```

## Load data

```{r load}

# For calculation, I use wavelengths between 390 and 780nm in steps of 2nm
wavelengths <- seq(390, 780, 2)

# Read data from Manchester
manchester <- data.table(read.xlsx(here("other_data", "all manchester spectra.xlsx")))
names(manchester)[1] <- "Wavelength"
fundamentals_manchester <- manchester[Wavelength >= 390, .(Wavelength, R, S, M, L)]
names(fundamentals_manchester) <- c("Wavelength", "rod", "scone", "mcone", "lcone")

led_spectra <- manchester[Wavelength >= 390, .(Wavelength, Red, Green, Blue, Amber)]

# Read fundamentals from Erlangen
load(here("data", "photoreceptor_sensitivities.rda"))
fundamentals_cord <- data.table(Wavelength = wavelengths, 
                                photoreceptor_spectral_sensitivities)
fundamentals_cord$melanopsin <- NULL

```

## Compare fundamentals graphically

The red lines are the fundamentals from Erlangen, the black lines from Manchester.

```{r}

ggplot(melt(fundamentals_manchester, id.vars = "Wavelength"), 
       aes(x = Wavelength, y = value, group = variable)) +
  geom_line() +
  geom_line(data = melt(fundamentals_cord, id.vars = "Wavelength"), color = "red")

```

## Comparison with the Stockman fundamentals

There is also a Stockman & Sharpe (2000) table ("2-deg fundamentals based on the Stiles & Burch 10-deg CMFs (adjusted to 2-deg)") on cvrl.org. The cone fundamentals from Jan's Excel sheet are apparently identical to the ones from Manchester and similar but not identical to these Stockman&Sharpe 2° fundamentals (green). The differ at lower wavelengths.

```{r}

data.table(Wavelength = wavelengths, analyzeTCS::ConeFundamentals2) %>%
  melt(id.vars = "Wavelength") %>%
  ggplot(aes(x = Wavelength, y = value, group = variable)) +
  geom_line(color = "green") +
  geom_line(data = melt(fundamentals_manchester, id.vars = "Wavelength"))

```

## LED spectra from Manchester

```{r}

ggplot(melt(led_spectra, id.vars = "Wavelength"), 
       aes(x = Wavelength, y = value, group = variable)) +
  geom_line() 

```

I'm not sure what luminances to use for calculating the spectra. However, this should not matter, so I will just pick 10cd/m^2 for each LED.

```{r}

led_luminances <- c(Red = 10, Amber = 10, Green = 10, Blue = 10)

p_led <- 
  led_spectra %>%
  get_normalized_spectrum_matrix() %>%
  calculate_power_spectra(luminances = led_luminances, spectra = .)



```

This results in the following LED powers [W/m^2].

```{r}

apply(p_led, 2, sum)

```

## Calculate A-Matrices

### Fundamentals from Erlangen

```{r}

print(create_A_matrix)

```
The main part of this function is:
*a_matrix <- crossprod(P_led, s_receptors)*

```{r}

s_receptors <- 
  fundamentals_cord %>%
  get_normalized_spectrum_matrix() 

p_led <- 
  led_spectra %>%
  get_normalized_spectrum_matrix() %>%
  calculate_power_spectra(luminances = led_luminances, spectra = .)

a_matrix_cord <- create_A_matrix(P_led = p_led, s_receptors = s_receptors)

print(a_matrix_cord)



```
In Jan's spreadsheet, the A-Matrix is normalized, so that all colums add up to one. As a consequence, calculations with photoreceptor contrasts should be possible.

```{r}

# Calculate column sums
apply(a_matrix_cord, 2, sum)

```

### Fundamentals from Manchester

```{r}

s_receptors <- 
  fundamentals_manchester %>%
  get_normalized_spectrum_matrix() 

p_led <- 
  led_spectra %>%
  get_normalized_spectrum_matrix() %>%
  calculate_power_spectra(luminances = led_luminances, spectra = .)

a_matrix_manchester <- create_A_matrix(P_led = p_led, s_receptors = s_receptors)

print(a_matrix_manchester)

```

## Compare resulting LED contrasts

LED contrasts are calculated by calculating the crossproduct of the photoreceptor contrasts and the inverse of the A-Matrix.

```{r}

print(find_LED_contrasts)

```

The main part of this function is:
*contrast_matrix <- crossprod(photoreceptor_contrasts, solve(A_matrix))*

### L-cone contrast of 10%

Comparison of the Michelson contrast in %. A negative signs means modulation in counterphase.

```{r}

find_LED_contrasts(c(lcone = .1, mcone = 0, rod = 0, scone = 0), a_matrix_cord) * 100

find_LED_contrasts(c(lcone = .1, mcone = 0, rod = 0, scone = 0), a_matrix_manchester) * 100

```
### M-cone contrast of 10%

Apparently, there is a considerable difference between calculations. Note that amber modulation is > 100% here, so that 10% M-cone contrast is above instrument gamut, but this should not matter here.

```{r}

find_LED_contrasts(c(lcone = 0, mcone = 0.1, rod = 0, scone = 0), a_matrix_cord) * 100

find_LED_contrasts(c(lcone = 0, mcone = 0.1, rod = 0, scone = 0), a_matrix_manchester) * 100

```
### Rod contrast of 10%

```{r}

find_LED_contrasts(c(lcone = 0, mcone = 0, rod = 0.1, scone = 0), a_matrix_cord) * 100

find_LED_contrasts(c(lcone = 0, mcone = 0, rod = 0.1, scone = 0), a_matrix_manchester) * 100

```

### S-cone contrast of 10%

```{r}

find_LED_contrasts(c(lcone = 0, mcone = 0, rod = 0, scone = 0.1), a_matrix_cord) * 100

find_LED_contrasts(c(lcone = 0, mcone = 0, rod = 0, scone = 0.1), a_matrix_manchester) * 100

```