---
title: "Test stimulus calculation"
output: html_notebook
---

```{r init, include=FALSE}

library(here)
i_am("R/test_calculations.Rmd")
source(here("R", "functions.R"))

```

# Own example

```{r}

l_mean <- c(20, 40, 3, 20)
P_LED <- calculate_power_spectra(l_mean, as.matrix(analyzeTCS::LED1[, -1]))
s_receptors <- as.matrix(ConeFundamentals10)

A_matrix <- 
  create_A_matrix(P_LED, s_receptors)

a <- find_LED_contrasts(c(rod = .1, scone = 0, mcone = 0, lcone = 0), A_matrix)
b <- findLEDContrasts(c(lcone = 0, mcone = 0, rod = 10, scone = 0), 
                      c(red = 20, green = 40, blue = 3, cyan = 20), 
                      ConeFundamentals10, FALSE)



```

# Find out what last step in old script does

```{r}

lmean <- c(20, 40, 3, 20)
A_matrix <- crossprod(as.matrix(LED1[, 2:5]), as.matrix(ConeFundamentals10))
rinput <- c()
for(i in 1:4) {
  rinput <- rbind(rinput, 2 * lum2nrg[i] * lmean[i] * A_matrix[i, ] / 100)
}
rinput2 <- t(t(rinput) / apply(rinput, 2, sum))

```

```{r}

P_LED <- as.matrix(analyzeTCS::LED1[, -1])
s_receptors <- as.matrix(ConeFundamentals10)

A_matrix <- 
  create_A_matrix(P_LED, s_receptors)

print(t(A_matrix)[c(2, 3, 4, 1), c(3, 4, 2, 1)])

```

```{r}

# scaling for max power range

a <- find_LED_contrasts(c(rod = 0, scone = 0, mcone = 1, lcone = 0), A_matrix)

max(abs(a))

crossprod(c(1, 1, 1, 1), matrix(1:16, nrow = 4))

crossprod(A_matrix, diag(4))
A_matrix

```

# Testing our formulas with the data from the Star Protocol

## Deriving the A-Matrix

## Using the A-Matrix

```{r load A-matrix from STAR, include = FALSE}

star_A_matrix <- 
  as.matrix(
    read.csv2(here("data", "star_A_matrix.csv"), row.names = 1)
  )

```

The excel sheet contains an unnecessary matrix mulplication with a diagonal vector. The product with the vectors (1, 0, 0, 0, 0), (0, 1, 0, 0, 0), basically picks single columns of the inverted A-matrix and allows identification of the largest absolute value.

```{r recapitulating calculations from excel}

print(star_A_matrix)

identical(solve(star_A_matrix), solve(star_A_matrix) %*% diag(5))

# Scaling for power range
A2 <- apply(solve(star_A_matrix), 
                         2, 
                         FUN = function(x) max(abs(x)))

max(abs(solve(star_A_matrix) %*% c(1, 0, 0, 0, 0))) == A2[1]

```


```{r}

max_power_range <- apply(solve(star_A_matrix), 
                         2, 
                         FUN = function(x) max(abs(x)))

# Rescale the inverted A-matrix
rescaled_inverted_A_matrix <- (matrix(c(1,1,1,1,1), ncol = 1) %*% (1/max_power_range)) * solve(star_A_matrix)

find_LED_contrasts(c(rod = .1, lcone = 0, scone = 0, mcone = 0, i = 0), star_A_matrix)

# rescale the star matrix, so that the sum becomes 1
rescaled_to_sum <- t(t(star_A_matrix) / apply(star_A_matrix, 2, sum))


```

The star protocoll rescales the A-matrix to a maximum value of 1, wheres the old protocol rescales to a sum of 1.