---
title: "Comparing MCVS and 4primary"
output: html_notebook
---

```{r}

library(jsonlite)
library(here)
library(data.table)
library(colorSpec)

i_am("R/comparison_with_4prim.Rmd")

mcvs <- read_json(here("inst", "213__AugeRechts_2024_07_05.json"), simplifyVector = TRUE)

```

# MCVS conditions

```{r mcvs illuminance}

mcvs_luminances <- mcvs$measurementData$data$preset$geometry$outerGeo$colour |>
  unique() |>
  unlist()

pupil_diameter_mm <- 8
pupil_area_mm2 <- pi * (pupil_diameter_mm / 2)^2

mcvs_cd_per_meter2 <- sum(mcvs_luminances) 
mcvs_troland <- mcvs_cd_per_meter2 * pupil_area_mm2

```

```{r mcvs chromaticity}

mcvs_specs <- colorSpec::readSpectra(here("data", "mcvs_spectra.csv"))

mcvs_specs$RED.LED <- 
  mcvs_specs$RED.LED * mcvs_luminances$red / photometric(mcvs_specs)["RED.LED", "photopic1978"]
mcvs_specs$GREEN.LED <- 
  mcvs_specs$GREEN.LED * mcvs_luminances$green / photometric(mcvs_specs)["GREEN.LED", "photopic1978"]
mcvs_specs$BLUE.LED <- 
  mcvs_specs$BLUE.LED * mcvs_luminances$blue / photometric(mcvs_specs)["BLUE.LED", "photopic1978"]
mcvs_specs$AMBER.LED <- 
  mcvs_specs$AMBER.LED * mcvs_luminances$amber / photometric(mcvs_specs)["AMBER.LED", "photopic1978"]
mcvs_specs$CYAN <- 
  mcvs_specs$CYAN * mcvs_luminances$cyan / photometric(mcvs_specs)["CYAN", "photopic1978"]

photometric(mcvs_specs)

mcvs_xyz <- product(mcvs_specs, xyz1964.1nm, wavelength = "auto") |>
  apply(2, sum)

mcvs_x <- mcvs_xyz[1] / sum(mcvs_xyz)
mcvs_y <- mcvs_xyz[2] / sum(mcvs_xyz)

```
# Four-primary conditions

```{r led4 illuminance}

pinhole_area_mm2 <- pi * 1.5^2

led4_trolands <- list(red = 63, green = 15, blue = 27, cyan = 15)
led4_trolands <- lapply(led4_trolands, function(x) return(x * 50 / 27))
led4_luminances <- lapply(led4_trolands, function(x) return(x / pinhole_area_mm2))

led4_cd_per_meter2 <- sum(unlist(led4_luminances))
led4_troland <- led4_cd_per_meter2 * pupil_area_mm2

```

```{r led4 chromaticity}

led4_specs <- colorSpec::readSpectra(here("data", "led4_spectra.csv"))

led4_specs$red <- 
  led4_specs$red * led4_luminances$red / photometric(led4_specs)["red", "photopic1978"]
led4_specs$green <- 
  led4_specs$green * led4_luminances$green / photometric(led4_specs)["green", "photopic1978"]
led4_specs$blue <- 
  led4_specs$blue * led4_luminances$blue / photometric(led4_specs)["blue", "photopic1978"]
led4_specs$cyan <- 
  led4_specs$cyan * led4_luminances$cyan / photometric(led4_specs)["cyan", "photopic1978"]

photometric(led4_specs)

led4_xyz <- product(led4_specs, xyz1964.1nm, wavelength = "auto") |>
  apply(2, sum)

led4_x <- led4_xyz[1] / sum(led4_xyz)
led4_y <- led4_xyz[2] / sum(led4_xyz)

```

Following these calculations, the illuminances in the LED stimulator will be set to red: 116,67, green: 27.8 (using a 0.3 neutral density filter), blue: 50, and cyan: 27.8 (again, with a 0.3 ND filter).

This results in a gamut for the L-cone stimulus of ~40% and for the L-cone stimulus of ~6%. The melanopsin contrast are negligible for L-cones, and ~8% of M-cone contrast for M-cone stimuli.
